---
title: "Merge data and export"
output:
  html_document:
    toc: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F)
library(tidyverse)
library(here)
library(ggplot2)
library(stringi)
library(redivis)
library(assertthat)

# source(here("data_helpers.R"))
DATA_LOC=here("harmonized_data")
```

Set up the function for getting tables. 

```{r}
get_tbl <- function(con = DATA_LOC, dataset_name, tbl_name) {
  # con is fake rn, and takes in the root dir for all datasets
  if (missing(dataset_name)) {
    stop("dataset_name must be provided")
  }
  if (missing(tbl_name)) {
    stop("tbl_name must be provided")
  }
  
  file_path <- file.path(con, dataset_name, paste0(tbl_name, ".csv"))
  if (!file.exists(file_path)) {
    stop(paste("File does not exist:", file_path))
  }
  
  out <- read_csv(file_path, show_col_types = FALSE)
  
  out
}
```

# Make tables


Mark with dataset IDs

```{r}
# options to get trials / choices / messages for all datasets
dataset_names <- list.dirs(DATA_LOC, full.names = FALSE) |> 
  stri_remove_empty()

dataset_names <- dataset_names[-8]
```



Messages

Table messages {
  id integer [primary key]
  
  trial_id integer [foreign key trials]
  player_id integer [foreign key players]
  dataset_id [foreign key datasets]

  role varchar 
  text string
  message_number integer
  message_irrelevant bool
  time_stamp time
}


```{r}
messages <- map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "messages") |>
                     mutate(dataset_id = d)) |> 
  filter(!is.na(text)) 

na_messages <- messages |> filter(if_any(c("player_id", "trial_id", "role", "message_number", "text", "dataset_id"), is.na))
assert_that(nrow(na_messages)==0)

```



Trials

Table trials {
  id integer [primary key]
  
  condition_id integer [foreign key conditions]
  dataset_id [foreign key datasets]
  option_set list [foreign key images]
  describer varchar [foreign key players]
  matchers list [foreign key matchers]
  
  game_id varchar
  
  room_num varchar
  target integer
  stage_num integer
  trial_num integer
  rep_num integer
  exclude bool
  exclusion_reason varchar

}

```{r}
trials <-   map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "trials") |> 
                     mutate(target = as.character(target),
                            matchers = as.character(matchers),
                            dataset_id = d)) #|> 
 # mutate(option_set = option_set |> 
  #         str_remove_all("\\[|\\]|\"") |> 
   #        str_replace_all(",", ";") )

na_trials <- trials |> filter(if_any(c("condition_id", "game_id", "room_num", "option_set", "target", "stage_num", "trial_num", "rep_num","describer", "dataset_id"), is.na))
assert_that(nrow(na_trials)==0)


```

Conditions & datasets


Table datasets{
  dataset_id [primary key]
  
  full_cite varchar
  short_cite varchar
}

Table conditions{
  id integer [primary key]
  dataset_id [foreign key datasets]
  
  group_size integer
  structure varchar
  language varchar
  placeholder_features varchar PLACEHOLDER
}


```{r}
conditions <- map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "conditions"))

datasets <- tibble(dataset_id = dataset_names) |>
  left_join(conditions |>
              select(dataset_id, full_cite, short_cite) |>
              distinct()) 

conditions <- conditions |>
  select(-full_cite, -short_cite)

na_datasets <- datasets |> filter(if_any(c("dataset_id", "full_cite", "short_cite"), is.na))
assert_that(nrow(na_datasets)==0)

na_conditions <- conditions |> filter(if_any(c("dataset_id", "condition_id", "group_size", "structure", "language"), is.na))
assert_that(nrow(na_conditions)==0)

```


Choices

Table choices {
  id integer [primary key]
  
  trial_id integer [foreign key trials]
  choice_id  [foreign key images]
  player_id integer [foreign key players]
  dataset_id [foreign key datasets]
  
  time_to_choice time 
}


```{r}
choices <- map_df(dataset_names, function (d) {
  df <- get_tbl(DATA_LOC, d, "choices")  |>
    mutate(player_id = as.numeric(player_id), 
           time_stamp = as.numeric(time_stamp),
           trial_id = as.numeric(trial_id),
           dataset_id = d) 
  
  df
}) 

na_choices <- choices |> filter(if_any(c("trial_id", "choice_id", "player_id", "dataset_id"), is.na))
assert_that(nrow(na_choices)==0)
```

Players

Table players {
  id integer [primary key]
  
  dataset_id [foreign key datasets]

  age integer
  gender varchar
  placeholder_demo varchar
}

```{r}
players <- map_df(dataset_names, function (d) {
  df <- get_tbl(DATA_LOC, d, "players") |> 
    mutate(player_id=as.numeric(player_id),
           dataset_id=d)
  
  df
})

na_players <- players |> filter(if_any(c("player_id", "dataset_id"), is.na))
assert_that(nrow(na_players)==0)
```

Images (already one table for all images)

Table images {
  image_id [primary key]
  
  kilogram_id varchar
  image_type varchar
  image_path varchar
}

```{r}
images <- read_csv(here("image_data/image_metadata.csv"))

# keep here!
na_images <- images |> filter(if_any(c("image_id", "image_type"), is.na))
assert_that(nrow(na_images)==0)


assert_that(nrow(trials |> select(target) |> unique() |> anti_join(images |> select(target=image_id)))==0)

options <- trials |> select(option_set) |> mutate(image_id = str_split(option_set, ";")) |> unnest(image_id) |> select(image_id) |> unique()

assert_that(nrow(images |> anti_join(options))==0)
```

# Create cross-dataset unique ids
(dataset id non-numeric)

* trials
* games
* players
* conditions

( * message id)
( * selection id)

( image id non-numeric )

```{r}
players_unique <- players |> ungroup() |> 
  mutate(player_id_num=row_number())

conditions_unique <- conditions |> ungroup() |> 
  mutate(condition_id_num=row_number())

games_unique <- trials |> ungroup() |> select(game_id, dataset_id) |> unique() |> 
  mutate(game_id_num=row_number())

trials_unique <-  trials |> ungroup() |> 
  left_join(players_unique |> select(dataset_id, describer=player_id, describer_id_num=player_id_num)) |> 
  mutate(matcher=str_split(matchers, ";")) |> unnest(matcher) |> 
  mutate(matcher=as.numeric(matcher)) |> 
  left_join(players_unique |> select(dataset_id, matcher=player_id, matcher_id_num=player_id_num)) |> 
  group_by(across(c(-matcher, -matcher_id_num))) |> 
  summarize(matchers_num=str_c(matcher_id_num, sep=";", collapse=";")) |> 
  left_join(games_unique) |> 
  left_join(conditions_unique) |> 
  ungroup() |> 
  mutate(trial_id_num=row_number())


messages_final <- messages |> left_join(trials_unique |> select(dataset_id, trial_id, trial_id_num)) |> 
  select(-trial_id) |> rename(trial_id=trial_id_num) |> 
  left_join(players_unique |> select(dataset_id, player_id, player_id_num)) |> 
  select(-player_id) |> rename(player_id=player_id_num) |> 
  ungroup() |> 
  mutate(message_id=row_number())

choices_final <- choices |> left_join(trials_unique |> select(dataset_id, trial_id, trial_id_num)) |> 
  select(-trial_id) |> rename(trial_id=trial_id_num) |> 
  left_join(players_unique |> select(dataset_id, player_id, player_id_num)) |> 
  select(-player_id) |> rename(player_id=player_id_num) |> 
  ungroup() |> 
  mutate(choices_id=row_number())

trials_final <- trials_unique |> 
  select(-trial_id, -game_id, -describer, -matchers, -condition_id) |> 
  rename(trial_id=trial_id_num, game_id=game_id_num, describer=describer_id_num, 
         matchers=matchers_num, condition_id=condition_id_num)

conditions_final <- conditions_unique |> select(-condition_id) |> rename(condition_id=condition_id_num)

players_final <- players_unique |> select(-player_id) |> rename(player_id=player_id_num)

  
```

# Validate more

```{r}
assert_that(length(players_final$player_id)==length(players$player_id))
assert_that(length(conditions_final$condition_id)==length(conditions$condition_id))
assert_that(length(choices_final$choices_id)==length(choices$choice_id))
assert_that(length(messages_final$message_id)==length(messages$message_number))
assert_that(length(trials_final$trial_id)==length(trials$trial_id))

assert_that(length(players_final$player_id)==length(players_final$player_id |> unique()))
assert_that(length(conditions_final$condition_id)==length(conditions_final$condition_id |> unique()))
assert_that(length(trials_final$trial_id)==length(trials_final$trial_id |> unique()))
assert_that(length(messages_final$message_id)==length(messages_final$message_id |> unique()))
assert_that(length(choices_final$choices_id)==length(choices_final$choices_id |> unique()))

assert_that(length(datasets$dataset_id)==length(datasets$dataset_id |> unique()))
assert_that(length(images$image_id)==length(images$image_id |> unique()))




```


# Export

Write out for redivis with missing for NA to facilitate import. 

```{r}
write_csv(datasets, here("export", "datasets.csv"), na = "")
write_csv(messages_final, here("export", "messages.csv"), na = "")
write_csv(choices_final,  here("export", "choices.csv"), na = "")
write_csv(trials_final, here("export", "trials.csv"), na = "")
write_csv(conditions_final, here("export", "conditions.csv"), na = "")
write_csv(players_final, here("export", "players.csv"), na="")
write_csv(images, here("export", "images.csv"), na="")
```

Now try pushing them directly to redivis. 

```{r}
# Set up the connection to Redivis

con <- redivis::user("mcfrank")$dataset("refbank:2zy7")

dataset <- con$create_next_version(if_not_exists=T)


dataset$table("datasets:q7yy")$update(upload_merge_strategy="replace")
dataset$table("messages:2q18")$update(upload_merge_strategy="replace")
dataset$table("choices:s1zj")$update(upload_merge_strategy="replace")
dataset$table("trials:zkj2")$update(upload_merge_strategy="replace")
dataset$table("conditions:kk1e")$update(upload_merge_strategy="replace")
dataset$table("players:7xnd")$update(upload_merge_strategy="replace")
dataset$table("images:jw0t")$update(upload_merge_strategy="replace")





upload <- dataset$table("datasets:q7yy")$upload()$create(
  "export/datasets.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("messages:2q18")$upload()$create(
  "export/messages.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("choices:s1zj")$upload()$create(
  "export/choices.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("trials:zkj2")$upload()$create(
  "export/trials.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("conditions:kk1e")$upload()$create(
  "export/conditions.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)


upload <- dataset$table("players:7xnd")$upload()$create(
  "export/players.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("images:jw0t")$upload()$create(
  "export/images.csv",
  type="delimited",        
  remove_on_fail = TRUE,     
  wait_for_finish = TRUE, 
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

dataset$release()

  # 
# upload <- table$upload()$create(
#     "./data.csv",           # Path to file, data.frame, raw vector, etc
#     type="delimited",       # Inferred from file extension if not provided
#     remove_on_fail=True,    # Remove the upload if a failure occurs
#     wait_for_finish=True,   # Wait for the upload to finish processing
#     raise_on_fail=True      # Raise an error on failure
# )
```

