---
title: "Merge data and export"
output:
  html_document:
    toc: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F)
library(tidyverse)
library(here)
library(ggplot2)
library(stringi)
library(redivis)
library(assertthat)

# source(here("data_helpers.R"))
DATA_LOC <- here("harmonized_data")
```

# Re-run imports scripts

```{r}
rerun_imports <- function(to_run){
# delete harmonized data
list.files(here("harmonized_data")) |> map(\(f){unlink(here("harmonized_data", f),recursive=T)})

source("validate.R")
Sys.setenv(FORCE_WRITE = "true")
to_run |> map(\(f){
  print(f)
  source(here("import", f, "import.R"))})
Sys.unsetenv("FORCE_WRITE")
source(here("import_images.R"))
}
```


```{r}
# to re-run
to_run <- c("yoon2019_audience", "wang2025_lvlms", "mankewitz2025_function","leung2024_scaffolding",
            "ji2025_adhoc", "hawkins2023_frompartners", "hawkins2021_respect", "hawkins2026_fmri",
            "hawkins2020_characterizing", "hawkins2019_continual",
            "dale2011_tangram", "branigan2016_doyouknow", "boyce2026_preschoolers",
            "boyce2024_interaction", "boegels2025_power", "dahan2023_collaboration",
            "bangerter2020_lexical", "bangerter2000_reuse", "beatty-martinez2026_tangrams")

rerun_imports(to_run)

```


# Make tables

Set up the function for getting tables. 

```{r}
get_tbl <- function(con = DATA_LOC, dataset_name, tbl_name) {
  # con is fake rn, and takes in the root dir for all datasets
  if (missing(dataset_name)) {
    stop("dataset_name must be provided")
  }
  if (missing(tbl_name)) {
    stop("tbl_name must be provided")
  }

  file_path <- file.path(con, dataset_name, paste0(tbl_name, ".csv"))
  if (!file.exists(file_path)) {
    stop(paste("File does not exist:", file_path))
  }

  out <- read_csv(file_path, show_col_types = FALSE)

  out
}
```



Mark with dataset IDs

```{r}
# options to get trials / selections / messages for all datasets
dataset_names <- list.dirs(DATA_LOC, full.names = FALSE) |>
  stri_remove_empty()
```



Messages

Table messages {
  id integer [primary key]

  trial_id integer [foreign key trials]
  player_id integer [foreign key players]
  dataset_id [foreign key datasets]

  role varchar
  text string
  message_num integer
  message_irrelevant bool
  time_stamp time
}


```{r}
messages <- map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "messages") |>
  mutate(dataset_id = d,
         player_id=as.numeric(player_id),
         message_num=as.numeric(message_num),
         message_irrelevant=as.logical(message_irrelevant),
         time_stamp=as.numeric(time_stamp),
         trial_id=as.numeric(trial_id))) |>
  filter(!is.na(text))

na_messages <- messages |> filter(if_any(c("player_id", "trial_id", "role", "message_num", "text", "dataset_id"), is.na))
assert_that(nrow(na_messages) == 0)

# newline characters can cause problems, so check!
newline_messages <- messages |> filter(str_detect(text, "\n"))
assert_that(nrow(newline_messages) == 0)

```



Trials

Table trials {
  id integer [primary key]

  condition_id integer [foreign key conditions]
  dataset_id [foreign key datasets]
  image_options list [foreign key images]
  describer varchar [foreign key players]
  matchers list [foreign key matchers]

  game_id varchar

  room_num varchar
  target_image integer
  stage_num integer
  trial_num integer
  round_num integer
  order_match varchar {order, match}
  exclude bool
  exclusion_reason varchar

}

```{r}
trials <- map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "trials") |>
  mutate(
    target_image = as.character(target_image),
    matchers = as.character(matchers),
    dataset_id = d
  )) #|>
# mutate(image_options = image_options |>
#         str_remove_all("\\[|\\]|\"") |>
#        str_replace_all(",", ";") )

na_trials <- trials |> filter(if_any(c("condition_id", "game_id", "room_num", "image_options", "target_image", "stage_num", "trial_num", "round_num", "describer", "dataset_id", "order_match"), is.na))
assert_that(nrow(na_trials) == 0)

trials <- trials |> mutate(option_set_size = image_options |> str_split(";") |>
  lengths())

assert_that(all(trials$trial_num > 0))
assert_that(all(trials$round_num > 0))
assert_that(all(trials$stage_num > 0))


assert_that(max(trials$option_set_size) == 36) # change these as datasets change, but we're trying to rule out screw ups that make it like 96 or something absurd
assert_that(min(trials$option_set_size) == 2)

assert_that(nrow(trials |> distinct(dataset_id, game_id, condition_id))==nrow(trials |> distinct(dataset_id, game_id)), msg="each game can have only one condition")
```

Conditions & datasets


Table datasets{
  dataset_id [primary key]
  
  full_cite varchar
  short_cite varchar
}

Table conditions{
  id integer [primary key]
  dataset_id [foreign key datasets]
  
  group_size integer
  language varchar
  population varchar {adult, child, child-parent} can have others if other atypical populations
  prior_relationship {yes,no}
  partner_constancy {yes,no}
  role_constancy {yes,no}
  confederates {yes, no}
  modality {written, oral-remote, oral-in-person}
  feedback {full, limited, none}
  backchannel {full, limited, none}
}


```{r}
conditions <- map_df(dataset_names, \(d) get_tbl(DATA_LOC, d, "conditions") |> mutate(condition_label=as.character(condition_label)))

datasets <- tibble(dataset_id = dataset_names) |>
  left_join(conditions |>
    select(dataset_id, full_cite, short_cite) |>
    distinct())

conditions <- conditions |>
  select(-full_cite, -short_cite)

na_datasets <- datasets |> filter(if_any(c("dataset_id", "full_cite", "short_cite"), is.na))
assert_that(nrow(na_datasets) == 0)

#conditions |> distinct(dataset_id, condition_label) |> View()
na_conditions <- conditions |> filter(if_any(c(
  "dataset_id", "condition_id", "group_size", "language", "prior_relationship", "partner_constancy", "population",
  "role_constancy", "confederates", "modality", "feedback", "backchannel", "condition_label"
), is.na))
assert_that(nrow(na_conditions) == 0)

assert_that(all(conditions$population %in% c("adult", "child", "child-parent")), msg="invalid population level")

conditions |> distinct(population, dataset_id) |> filter(!population %in% c("adult", "child", "child-parent"))
```


Selections

Table selections {
  selection_id integer [primary key]

  trial_id integer [foreign key trials]
  selected_image  [foreign key images]
  player_id integer [foreign key players]
  dataset_id [foreign key datasets]

  time_to_choice time
}


```{r}
selections <- map_df(dataset_names, function(d) {
  df <- get_tbl(DATA_LOC, d, "selections") |>
    mutate(
      player_id = as.numeric(player_id),
      time_stamp = as.numeric(time_stamp),
      trial_id = as.numeric(trial_id),
      selected_image =as.character(selected_image),
      dataset_id = d
    )

  df
})

na_selections <- selections |> filter(if_any(c("trial_id", "selected_image", "player_id", "dataset_id"), is.na))
assert_that(nrow(na_selections) == 0)
```

Players

Table players {
  id integer [primary key]
  
  dataset_id [foreign key datasets]

  age integer
  gender varchar
  native_language varchar
  race varchar
  education varchar
}

```{r}
players <- map_df(dataset_names, function(d) {
  df <- get_tbl(DATA_LOC, d, "players") |>
    mutate(
      player_id = as.numeric(player_id),
      dataset_id = d
    )

  df
})

  assert_that(
    all(is.na(players$education) |
      players$education %in% c("less-than-high-school", "high-school", "some-college", "bachelors", "advanced-degree")),
    msg = "education level options are less-than-high-school, high-school, some-college, bachelors, advanced-degree"
  )
na_players <- players |> filter(if_any(c("player_id", "dataset_id"), is.na))
assert_that(nrow(na_players) == 0)
```

Images (already one table for all images)

Table images {
  image_id [primary key]
  
  kilogram_id varchar
  image_type varchar
  image_path varchar
}

```{r}
images <- read_csv(here("image_data/image_metadata.csv"))

# keep here!
na_images <- images |> filter(if_any(c("image_id", "image_type"), is.na))
assert_that(nrow(na_images) == 0)


assert_that(nrow(trials |> select(target_image) |> unique() |> anti_join(images |> select(target_image = image_id))) == 0)


trials |> select(target_image, dataset_id) |> unique()  |> anti_join(images |> select(target_image = image_id))
options <- trials |>
  select(image_options) |>
  mutate(image_id = str_split(image_options, ";")) |>
  unnest(image_id) |>
  select(image_id) |>
  unique()

assert_that(nrow(images |> anti_join(options)) == 0)

images |> anti_join(options)
```

# Create cross-dataset unique ids
(dataset id non-numeric)

* trials
* games
* players
* conditions

( * message id)
( * selection id)

( image id non-numeric )

```{r}
players_unique <- players |>
  ungroup() |>
  mutate(player_id_num = row_number())

conditions_unique <- conditions |>
  ungroup() |>
  mutate(condition_id_num = row_number())

games_unique <- trials |>
  ungroup() |>
  select(game_id, dataset_id) |>
  unique() |>
  mutate(game_id_num = row_number())

trials_unique <- trials |>
  ungroup() |>
  left_join(players_unique |> select(dataset_id, describer = player_id, describer_id_num = player_id_num)) |>
  mutate(matcher = str_split(matchers, ";")) |>
  unnest(matcher) |>
  mutate(matcher = as.numeric(matcher)) |>
  left_join(players_unique |> select(dataset_id, matcher = player_id, matcher_id_num = player_id_num)) |>
  group_by(across(c(-matcher, -matcher_id_num))) |>
  summarize(matchers_num = str_c(matcher_id_num, sep = ";", collapse = ";")) |>
  left_join(games_unique) |>
  left_join(conditions_unique |> select(condition_id_num, condition_id, dataset_id)) |>
  ungroup() |>
  mutate(trial_id_num = row_number())


messages_final <- messages |>
  left_join(trials_unique |> select(dataset_id, trial_id, trial_id_num)) |>
  select(-trial_id) |>
  rename(trial_id = trial_id_num) |>
  left_join(players_unique |> select(dataset_id, player_id, player_id_num)) |>
  select(-player_id) |>
  rename(player_id = player_id_num) |>
  ungroup() |>
  mutate(message_id = row_number())

selections_final <- selections |>
  left_join(trials_unique |> select(dataset_id, trial_id, trial_id_num)) |>
  select(-trial_id) |>
  rename(trial_id = trial_id_num) |>
  left_join(players_unique |> select(dataset_id, player_id, player_id_num)) |>
  select(-player_id) |>
  rename(player_id = player_id_num) |>
  ungroup() |>
  mutate(selection_id = row_number())

trials_final <- trials_unique |>
  select(-trial_id, -game_id, -describer, -matchers, -condition_id) |>
  rename(
    trial_id = trial_id_num, game_id = game_id_num, describer = describer_id_num,
    matchers = matchers_num, condition_id = condition_id_num
  )

conditions_final <- conditions_unique |>
  select(-condition_id) |>
  rename(condition_id = condition_id_num)

players_final <- players_unique |>
  select(-player_id) |>
  rename(player_id = player_id_num)
```

# Validate more

```{r}
assert_that(length(players_final$player_id) == length(players$player_id))
assert_that(length(conditions_final$condition_id) == length(conditions$condition_id))
assert_that(length(selections_final$selection_id) == length(selections$selected_image))
assert_that(length(messages_final$message_id) == length(messages$message_num))
assert_that(length(trials_final$trial_id) == length(trials$trial_id))

assert_that(length(players_final$player_id) == length(players_final$player_id |> unique()))
assert_that(length(conditions_final$condition_id) == length(conditions_final$condition_id |> unique()))
assert_that(length(trials_final$trial_id) == length(trials_final$trial_id |> unique()))
assert_that(length(messages_final$message_id) == length(messages_final$message_id |> unique()))
assert_that(length(selections_final$selection_id) == length(selections_final$selection_id |> unique()))

assert_that(length(datasets$dataset_id) == length(datasets$dataset_id |> unique()))
assert_that(length(images$image_id) == length(images$image_id |> unique()))
```


# Export

Write out for redivis with missing for NA to facilitate import. 

```{r}
write_csv(datasets, here("export", "datasets.csv"), na = "")
write_csv(selections_final, here("export", "selections.csv"), na = "")
write_csv(trials_final, here("export", "trials.csv"), na = "")
write_csv(conditions_final, here("export", "conditions.csv"), na = "")
write_csv(players_final, here("export", "players.csv"), na = "")
write_csv(images, here("export", "images.csv"), na = "")


write_csv(messages_final, here("export", "messages.csv"), na = "")

```


Now try pushing them directly to redivis. 

```{r}
# Set up the connection to Redivis

con <- redivis$organization("datapages")$dataset("refbank:2zy7")

dataset <- con$create_next_version(if_not_exists = T)




dataset$table("datasets:q7yy")$update(upload_merge_strategy = "replace")
dataset$table("messages:2q18")$update(upload_merge_strategy = "replace")
dataset$table("selections:s1zj")$update(upload_merge_strategy = "replace")
dataset$table("trials:zkj2")$update(upload_merge_strategy = "replace")
dataset$table("conditions:kk1e")$update(upload_merge_strategy = "replace")
dataset$table("players:7xnd")$update(upload_merge_strategy = "replace")
dataset$table("images:jw0t")$update(upload_merge_strategy = "replace")


dataset$table("cosine_similarities:cp0s")$update(upload_merge_strategy= "replace")
dataset$table("embeddings:ckdc")$update(upload_merge_strategy= "replace")
dataset$table("per_game_summary:bsw0")$update(upload_merge_strategy= "replace")
dataset$table("summary:w9sc")$update(upload_merge_strategy= "replace")

upload <- dataset$table("datasets:q7yy")$upload()$create(
  "export/datasets.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("messages:2q18")$upload()$create(
  "export/messages.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("selections:s1zj")$upload()$create(
  "export/selections.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("trials:zkj2")$upload()$create(
  "export/trials.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("conditions:kk1e")$upload()$create(
  "export/conditions.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)


upload <- dataset$table("players:7xnd")$upload()$create(
  "export/players.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

upload <- dataset$table("images:jw0t")$upload()$create(
  "export/images.csv",
  type = "delimited",
  remove_on_fail = TRUE,
  wait_for_finish = TRUE,
  raise_on_fail = TRUE,
  replace_on_conflict = TRUE
)

# image files
upload <- dataset$table("image_files:zkvc")$add_files(
  directory = here("image_data/images/")
)
```

THIS IS WHERE YOU GO RUN THE WORKFLOW IN THE GUI TO GENERATE DERIVED TABLES!

```{r, eval=F}
# did you run the workflow?

con <- redivis$organization("datapages")$dataset("refbank:2zy7")
dataset <- con$create_next_version(if_not_exists = T)


# dataset$table("annotations")$create()
# dataset$table("parsed")$create()


dataset$release()
```


